master thesis

### 2018-03-12 Paper - Latex/Paper - Skizze - v3.tex
analyse Effects of unknown data models

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \section{Multifurcation}\label{sec:ResultsMultifurcation}
      One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
        binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
        since we only work with a synthesis tree, this tree is multifurcated: we have 241 974 internal 
        nodes and 2 293 463 leaf nodes. \\
      For a first overview we collected for every node its number of children (degree $-1$), and plotted
        this in an histogram, see figure \ref{fig:childrenOfNodes}. The multifurcation affects only the
        internal nodes. We collected the number of children $-2$ of every node (a node with two children 
        is binary). 
      \begin{wrapfigure}{r}{0.6\textwidth}
        \begin{center}
          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.58\textwidth]{Figures/multifurc.pdf}
        \end{center}
        \caption{Histogram about the multifurcation of the internal nodes of the synthesis tree. \\ 
          light blue: binary; dark blue: multifunction}
        \label{fig:childrenOfNodes}
      \end{wrapfigure}
      That means it discribes the number of nodes which we have lost from the real (binary) 
      phylogenetic tree. \\
      As you can see, we are very far from a binary tree.

@@

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            multifurc $\sim$ taxa & 545740 & 499227 & 482265 & XXXXX\\
            \hline
            multifurc $\sim$ taxa + depth & 544789 & 493017 & XXXXX & XXXXX \\
            \hline
            multifurc $\sim$ taxa * depth & 544062 & 488366 & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Residuals of unknown information}
        \label{table:...} 
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            multifurc $\sim$ taxa & 545799 & 500004 & 485121 & XXXXX\\
            \hline
            multifurc $\sim$ taxa + depth & 544862 & 493808 & XXXXX & XXXXX \\
            \hline
            multifurc $\sim$ taxa * depth & 544179 & 489845 & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BIC of unknown information}
        \label{table:BIC unknown information} 
      \end{table}

@@

      With the Nematoda it looks very different. In the Nematoda its much worse. Most Nematoda are 
        free-living, but we found only 2.63\% of them. Blaxter et al. speaks of at least seven 
        independently arosed parasitism \cite{Blaxter1998}. \\
        The problem at this point, however, is obvious: The parasites have been much more studied and 
        thus we start with only 0.63\% free-living species. Against such a shifted data situation, the 
        algorithm is almost powerless. And yet the percentage has increased.

@@

    \anmerkung{different parameters for different taxa? (Emanuel) -> Effects...} \\ \\

@@

    \begin{table}[h!]
      \begin{center}
        \begin{longtable}{ |l|l|r|r|r| }
          \hline
          \multicolumn{2}{|c|}{Taxa / Model} & globi $\sim$ taxa & globi $\sim$ taxa + depth & globi $\sim$ taxa * depth\\
          \hline \hline
          Kingdom & no kingdom  & 0.007608091 & 0.009900630 & 0.0004645054 \\
          & Fungi               & 0.011317000 & 0.013723310 & 0.0064413062 \\
          & Chloroplastida      & 0.008634310 & 0.008018847 & 0.0058472786 \\
          & Metazoa             & 0.035634187 & 0.034139782 & 0.0343237575 \\
          \hline
          Phylum & no phylum    & 1.569769e-02 & 3.001749e-02 & 5.757839e-03 \\
          & Rhombozoa           & 1.538462e-02 & 4.128162e-02 & 1.000000e+00 \\
          & Hemichordata        & 1.736770e-07 & 3.791496e-07 & 1.736742e-07 \\
          & Chromerida          & 1.736770e-07 & 4.605436e-07 & 2.220446e-16 \\
          & Amoebozoa           & 5.343198e-03 & 1.312565e-02 & 2.401619e-03 \\
          & Onychophora         & 1.736770e-07 & 3.663718e-07 & 1.736753e-07 \\
          & ... & ... & ... & ... \\
          % & Priapulida          & 4.347826e-02 & 8.773029e-02 \\
          % & Tardigrada          & 1.736770e-07 & 3.393298e-07 \\
          % & Chordata            & 1.140600e-01 & 8.242171e-02 \\
          % & Xanthophyceae       & 1.736770e-07 & 3.483928e-07 \\
          % & Haptophyta          & 3.484321e-03 \\
          % & Microsporidia       & 8.703271e-02 \\
          % & Chytridiomycota     & 3.062361e-02 \\
          % & Nematomorpha        & 1.495017e-02 \\
          % & Loricifera          & 1.736770e-07 \\
          % & Gnathostomulida     & 1.736770e-07 \\
          % & Myzostomida         & 4.464286e-03 \\
          % & Gastrotricha & 1.736770e-07 \\
          % & Ciliophora & 8.372371e-03 \\
          % & Entoprocta & 1.736770e-07 \\
          % & Glomeromycota & 6.609385e-04 \\
          % & Nematoda & 1.098682e-01 \\
          % & Cycliophora & 1.736770e-07 \\
          % & Apicomplexa & 1.374128e-01 \\
          % & Ascomycota & 1.232671e-02 \\
          % & Bryozoa & 4.194290e-03 \\
          % & Nemertea & 9.465855e-03 \\
          % & Echinodermata & 1.971448e-02 \\
          % & Rotifera & 8.638563e-03 \\
          % & Picozoa & 1.736770e-07 \\
          % & Phaeophyceae & 1.219884e-03 \\
          % & Acanthocephala & 3.935018e-01 \\
          % & Bacillariophyta & 4.757374e-05 \\
          % & Colponemidia & 1.736770e-07 \\
          % & Platyhelminthes & 3.127011e-01 \\
          % & Entorrhizomycota & 1.736770e-07 \\
          % & Chaetognatha & 2.941176e-02 \\
          % & Placozoa & 1.736770e-07 \\
          % & Euglenida & 1.729107e-03 \\
          % & Arthropoda & 2.506545e-02 \\
          % & Basidiomycota & 6.149777e-03 \\
          % & Cnidaria & 1.928587e-02 \\
          % & Ctenophora & 4.205607e-02 \\
          % & Kinorhyncha & 1.736770e-07 \\
          % & Porifera & 7.720212e-03 \\
          % & Orthonectida & 1.153846e-01 \\
          % & Mollusca & 9.876095e-03 \\
          % & Brachiopoda & 6.920415e-03 \\
          % & Haplosporida & 8.108108e-02 \\
          % & Rhodophyta & 1.971220e-04 \\
          % & Streptophyta & 8.901842e-03 \\
          % & Foraminifera & 3.395201e-04 \\
          % & Chlorophyta & 3.084992e-04 \\
          \hline \hline
          \multicolumn{2}{|c|}{Taxa / Model} & correct predicted & correct predicted & correct predicted \\
          \multicolumn{2}{|c|}{} & $\sim$ taxa & $\sim$ taxa + depth & $\sim$ taxa * depth \\
          \hline \hline
          Kingdom & no kingdom  & 0.001139888 & ... & ... \\
          & Fungi               & 0.001789739 & ... & ... \\
          & Chloroplastida      & 0.001251109 & ... & ... \\
          & Metazoa             & 0.005414443 & ... & ... \\
          % \hline
          % Phylum & no phylum    & XXXXX & 3.001749e-02 & 5.757839e-03 \\
          % & Rhombozoa           & XXXXX & 4.128162e-02 & 1.000000e+00 \\
          % & Hemichordata        & XXXXX & 3.791496e-07 & 1.736742e-07 \\
          % & Chromerida          & XXXXX & 4.605436e-07 & 2.220446e-16 \\
          % & Amoebozoa           & XXXXX & 1.312565e-02 & 2.401619e-03 \\
          % & Onychophora         & XXXXX & 3.663718e-07 & 1.736753e-07 \\
          % & ... & ... & ... & ... \\
          \hline
        \end{longtable} 
      \end{center}
      \caption{Effects of Taxa in models for unknown data}
      \label{table:Effects unknown data} 
    \end{table}

@@

%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
%                       1.023682e-02                       2.297956e-01
%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
%                       8.586035e-02                       3.000311e-02
%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
%                       3.538708e-07                       3.160858e-07
%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
%                       9.396517e-03                       3.335103e-07
%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
%                       2.114329e-02                       3.281554e-07
%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
%                       1.687966e-03                       1.582959e-01
%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
%                       3.160858e-07                       2.849943e-01
%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
%                       2.217673e-02                       7.020371e-03
%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
%                       1.640797e-02                       3.399753e-02
%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
%                       1.516272e-02                       6.032169e-07
%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
%                       2.014280e-03                       5.672835e-01
%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
%                       1.048765e-04                       5.155971e-07
%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
%                       4.271198e-01                       4.449469e-07
%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
%                       5.936368e-02                       4.965510e-07
%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
%                       4.727403e-03                       1.935197e-02
%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
%                       1.149917e-02                       3.192464e-02
%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
%                       1.077673e-01                       3.540771e-07
%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
%                       1.613863e-02                       2.716252e-01
%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
%                       1.372700e-02                       1.079344e-02
%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
%                       1.925711e-01                       5.358571e-04
%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
%                       6.529378e-03                       7.447417e-04
%       ['ott979501', 'Chlorophyta']
%                       7.296356e-04

% ['ott1085175', 'Priapulida']        ['ott111438', 'Tardigrada']
%                       1.000000e+00                       1.736778e-07
%          ['ott125642', 'Chordata']     ['ott151001', 'Xanthophyceae']
%                       1.138205e-01                       1.736786e-07
%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
%                       1.000000e+00                       9.998257e-01
%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
%                       1.000000e+00                       2.220446e-16
%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
%                       2.220446e-16                       2.220446e-16
%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
%                       4.381889e-06                       1.736782e-07
%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
%                       5.518629e-05                       1.736802e-07
%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
%                       9.966669e-01                       4.725574e-01
%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
%                       2.220446e-16                       8.049756e-01
%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
%                       1.541511e-02                       1.230174e-03
%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
%                       1.777755e-01                       2.505179e-03
%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
%                       3.125183e-01                       1.736782e-07
%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
%                       9.252076e-04                       3.992551e-04
%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
%                       1.114784e-10                       2.220446e-16
%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
%                       2.478056e-02                       1.736781e-07
%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
%                       1.000000e+00                       4.021433e-08
%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
%                       9.257999e-01                       1.658528e-02
%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
%                       1.473459e-03                       1.218008e-02
%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
%                       2.878555e-03                       1.736844e-07
%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
%                       1.329787e-02                       2.931611e-02
%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
%                       5.167513e-03                       9.974617e-01
%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
%                       9.999999e-01                       9.658119e-11
%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
%                       6.037565e-03                       6.367782e-03
%       ['ott979501', 'Chlorophyta']
%                       2.027010e-05

>>>>

  In den Bacteria und Archaea wurde das mal allgemein für binary traits gemacht:
  "A total 90\% of all binary traits described molecular functions, specifically the presence or absence of a gene or a set of gene involved in biochemical pathways."
  \cite{Goberna2015} \\
  Unterschied bei uns ist parasitismus komplexer.. da sind meist nicht einzelne Gene zuständig..

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \section{Multifurcation}\label{sec:ResultsMultifurcation}
      One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
        binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
        since we only work with a synthesis tree, this tree is multifurcated: we have 241 974 internal 
        nodes and 2 293 463 leaf nodes. \\
      \begin{figure}[h]
        \centering
        \begin{subfigure}[b]{0.5\textwidth}
          \includegraphics[width=\textwidth]{Figures/multifurc.pdf}
          \caption{Histogram with automatic binwidth. \\ ~ \\ ~}
        \end{subfigure}
        ~~~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.42\textwidth}
          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=\textwidth]{Figures/multifurc_small.pdf}
          \caption{Histogram with $binwidth = 1$. \\ light blue: binary; dark blue: multifunction}
        \end{subfigure}
        \caption{Histograms about the multifurcation of the internal nodes of the synthesis tree.}
        \label{fig:childrenOfNodes}
      \end{figure}

      For a first overview we collected for every node its number of children (degree $-1$), and plotted
        this in two histograms, see figure \ref{fig:childrenOfNodes}. \\
      The multifurcation affects only the internal nodes. We collected the number of children $-2$ of 
        every node (a node with two children is binary). That means it discribes the number of nodes which we have lost from the real (binary) 
      phylogenetic tree. \\
      As you can see, we are very far from a binary tree.

@@

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class \\
            \hline \hline
            multifurc $\sim$ taxa & 545740 & 499227 & 482265 \\
            \hline
            multifurc $\sim$ taxa + depth & 544789 & 493017 & XXXXX \\
            \hline
            multifurc $\sim$ taxa * depth & 544062 & 488366 & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Residuals of unknown information}
        \label{table:...} 
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class \\
            \hline \hline
            multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 \\
            \hline
            multifurc $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 \\
            \hline
            multifurc $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!50}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BIC of unknown information}
        \label{table:BIC unknown information} 
      \end{table}

      \todo{Taxa like order or family were too expensive to calculate...}

@@

      With the Nematoda it looks very different. In the Nematoda its much worse. Most Nematoda are 
        free-living, but we found only 2.63\% of them. Blaxter et al. speaks of at least seven 
        independently arosed parasitism \cite{Blaxter1998}. In a recent article Blaxter identifies 18 
        origins \cite{Blaxter2015} in Nematoda. \\
        The problem at this point, however, is obvious: The parasites have been much more studied and 
        thus we start with only 0.63\% free-living species. Against such a shifted data situation, the 
        algorithm is almost powerless. And yet the percentage has increased.

        The evolution of parasitism in Nematoda: \\
        "while only approximately 23 000 species have been described (J. Hallan, unpublished; https://insects.tamu.edu/research/collection/hallan/), the true species-level diversity may be 1 million or more (Lambshead, 1993)." \\
        " Estimates of the number of species of parasitic nematode per host suggest that there may be of the order of 25 000 nematode parasites just of vertebrates, most of which remain undescribed (Dobson et al. 2008)" \\
        "a large proportion of nematode species may be parasites." \cite{Blaxter2015} \\

@@

@@

    \begin{table}[h!]
      \begin{center}
        \begin{tabular}{ |l|l|r|r|r|r| }
          \hline
          Taxa & Model / Effects & min & max & mean & median \\
          \hline \hline
          Kingdom & globi $\sim$ taxa & 0,01 & 0,04 & 0,02 & 0,01 \\
          & globi $\sim$ taxa + depth & 0,01 & 0,03 & 0,02 & 0,01 \\
          & globi $\sim$ taxa * depth & 0,00 & 0,03 & 0,01 & 0,01 \\
          \hline
          Phylum & globi $\sim$ taxa & 0,17 & 393501,80 & 32208,79 & 6149,78 \\
          & globi $\sim$ taxa + depth & 0,32 & 567010,90 & 55149,54 & 10783,18 \\
          & globi $\sim$ taxa * depth & 0,00 & 1000000,00 & 225375,33 & 2511,58 \\
          % \hline
          % Class & globi $\sim$ taxa & 0,10 & 628190,10 & 44684,53 & 1491,77 \\
          % & globi $\sim$ taxa + depth &  &  &  &  \\
          % & globi $\sim$ taxa * depth &  &  &  &  \\
          \hline
        \end{tabular} 
      \end{center}
      \caption{Effects of Taxa in models for unknown data}
      \label{table:Effects unknown data} 
    \end{table}

@@
